DOM Review Stats and Figures

### 2024-08-28 Analysis/ReviewFigures/Final_Figures.qmd
Re-rendered figures

```{r Taxa bar plot}
focalTaxaPlot <- sheet_FocalTaxa |>
  mutate(Status = case_when(Status %in% c("CR", "EN", "NT", "VU", "Threatened_Other") ~ "Threatened",
                            Status == "NA" ~ "Multiple species",
                            Status == "Invasive" ~ "Invasive",
                            Status == "LC" ~ "Stable")) |>
  mutate(Status = fct(Status, levels = c("Multiple species", "Invasive",
                                         "Stable", "Threatened"))) |>
  summarise(Articles = n(), .by = c(`Taxa keywords`, Status)) |>
  select(Articles, Taxa = `Taxa keywords`, Status) |>
  mutate(Taxa = case_when(Taxa == "NA" ~ "Other", .default = Taxa)) |>
  mutate(Taxa = fct(Taxa, levels = rev(c("Bird", "Mammal", "Herptile",
                                     "Invertebrate", "Other")))) |>

>>>>

```{r Taxa bar plot}
focalTaxaPlot <- sheet_FocalTaxa |>
  mutate(Status = case_when(Status %in% c("CR", "EN", "NT", "VU", "Threatened_Other") ~ "Threatened",
                            Status == "NA" ~ "Multiple species",
                            Status == "Invasive" ~ "Invasive",
                            Status == "LC" ~ "Stable")) |>
  mutate(Status = fct(Status, levels = c("Multiple species", "Invasive",
                                         "Stable", "Threatened"))) |>
  summarise(Articles = n(), .by = c(`Taxa keywords`, Status)) |>
  select(Articles, Taxa = `Taxa keywords`, Status) |>
  mutate(Taxa = case_when(Taxa == "NA" ~ "Other", .default = Taxa)) |>
  mutate(Taxa = fct(Taxa, levels = rev(c("Bird", "Mammal", "Herptile",
                                         "Fish", "Invertebrate", "Other")))) |>
